### 2021-10-11 content/80.formal-definition.tex
text mode in math mode in text mode.
Latex....

Notable from this triple-like formalization is that a RO-Crate $R$ is fully represented as a tree at depth 2 helped by the use of $𝕀𝕣𝕚$ nodes. For instance the aggregation from the root entity $hasPart(…interviews/>)$ is at same level as the data entity’s property $license(…CC-BY-NC-4.0>)$ and that contextual entity’s attribute name $(…Non Commercial 4.0”)$. As shown in section RO-Crate JSON-LD, the RO-Crate Metadata File serialization is an equivalent shallow tree, although at depth 3 to cater for the JSON-LD preamble of \texttt{"@context"} and \texttt{"@graph"}.

>>>>

Notable from this triple-like formalization is that a RO-Crate $R$ is fully represented as a tree at depth 2 helped by the use of $𝕀𝕣𝕚$ nodes. For instance the aggregation from the root entity $hasPart(\texttt{…interviews/>})$ is at same level as the data entity’s property $license(\texttt{…CC-BY-NC-4.0>})$ and that contextual entity’s attribute name $(\text{…Non Commercial 4.0”})$. As shown in section RO-Crate JSON-LD, the RO-Crate Metadata File serialization is an equivalent shallow tree, although at depth 3 to cater for the JSON-LD preamble of \texttt{"@context"} and \texttt{"@graph"}.
